---
title: "MIS data checks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}

#---- Load libraries (each time R restarts)
library(tidyverse)
library(janitor)
library(readxl)
library(sf)
library(openxlsx)
library(ggrepel)
library(here)
library(lubridate)
library(flextable)
library(officer)
library(labelled)
library(haven)

#---- Knitr options
knitr::opts_chunk$set(echo = TRUE)

```

```{r getdata}
#--- Read in the raw data dumped into the "raw" folder by the script that pulls from the ODK server
# It is set up this way to avoid having to pull from the server every time we knit

hh <- read.csv(here("pratica/raw/hh.csv"))
hhm <- read.csv(here("pratica/raw/hhm.csv"))
women <- read.csv(here("pratica/raw/women.csv"))
births <- read.csv(here("pratica/raw/births.csv"))
#birthcheck <- read.csv(here("pratica/raw/birthcheck.csv"))
fever <- read.csv(here("pratica/raw/fever.csv"))
biomarkers <- read.csv(here("pratica/raw/biomarkers.csv"))
nets <- read.csv(here("pratica/raw/nets.csv"))

# Set up small dataframe with hh details to add to other datasets
tb <- hh %>% select(id, surveyor_id, area, local, hh_nb, hh_id_field, date_today) %>%
  rename(submissions_id = id) # rename uuid to match the names in the repeat dataframes
tb$date_today <- as.Date(ymd_hms(tb$date_today))  # Fix date format

```

# Household data

```{r hhcheck}
#---- Household checks -----
hh_check <- hh %>% 
  mutate(starttime=as_datetime(start_survey),
         endtime=as_datetime(end_survey),
         startdate=date(starttime),
         enddate=date(endtime)) 

hh_check %>%  
  tabyl(startdate) 
hh_check %>% 
  tabyl(enddate)

# Check interviewer numbers
hh %>% tabyl(surveyor_id)
hh %>% tabyl(area)

# Check duplicate hhids
dupes <- hh_check %>%
  filter(startdate>"2023-10-3") %>% 
  group_by(hh_id_field) %>%
  filter(n()>1) %>%
  ungroup()

# Check head of household names in the duplicate HHIDs
dupes %>% tabyl(hhh)

# Check # of mosq nets
hh %>% tabyl(nb_mosq_nets)

hh %>% tabyl(nonet_g_no_net_reason_other)

hh %>% tabyl(final_comments)

# Does surveyor ID digit line up with hh ID number - problem with tablets going backwards/forwards

```

# Household members

```{r hhmcheck}

#----- Household Member Checks ----

hhm %>% tabyl(sex)
hhm %>% tabyl(live)
hhm %>% tabyl(age) # maybe an age pyramid? Check for 98s
hhm %>% tabyl(fever)
hhm %>% tabyl(travel)

```


# Fever

```{r fevars}
#fever <- read.csv(here("raw/fever.csv"))
# Join with hh details
fever <- left_join(fever, tb, by = "submissions_id")
# Remove Sunrise data
fever <- fever %>% filter(date_today > as.Date("2023-10-02"))

# Separate multiple choice var; this is janky AF there must be a better way...
fevexp = fever %>% mutate(medication_type = strsplit(medication_type, " ")) %>% 
  unnest(medication_type) %>% # Split up using space as seperator 
  mutate(medication_type = paste0("med_", medication_type),  # Add med_ prefix so var names won't cause pain
         medication_type = fct_expand(medication_type, "med_1", "med_2", "med_3", "med_4", "med_5", "med_6", "med_7", "med_8", "med_9", "med_10", "med_11", "med_12", "med_13", "med_14", "med_96", "med_98", "med_NA"), # add all factor levels (even ones that aren't in the data)
         count = 1) %>% # Create a count var that indicates that response was present in the data
  select(id, medication_type, count) %>% # Select only relevant vars
  complete(id, medication_type) %>% # Now add in rows for empty levels
  replace(is.na(.), 0) %>% # Replace NAs with 0
  pivot_wider(names_from = medication_type, values_from = count) %>% # Pivot wider
  select(id, med_1, med_2, med_3, med_4, med_5, med_6, med_7, med_8, med_9, med_10, med_11, med_12, med_13, med_14, med_96, med_98) # Can drop the NA here

# 1	= Artemisinin-based combination therapy (tca/coartem)
# 2	=	Sp/fansidar
# 3	=	Chloroquine
# 4	=	Amodiaquine
# 5	=	Quinine met
# 6	=	Quinine injection/iv
# 7	=	Suppository artesunate
# 8	=	Artesunate injection/iv
# 9	=	Another anti-malarial
# 10 =	Antibiotics pill/syrup
# 11	=	Injection/iv antibiotics
# 12	=	Other Aspirin Medications
# 13	=	Other paracetemol medicines
# 14	=	Other ibuprofen medications
# 96	=	Other
# 98	=	Do not know

# Add back into data  
fever <- left_join(fever, fevexp, by = "id")
# Remove the temp stuff
rm(fevexp)

```

```{r fevcheck}
#--- Data quality check
# If sought treatment, location of treatment
fever %>% tabyl(fever_treatment, treatment_place)
# Did they have a malaria test if they didn't seek treatment?
fever %>% tabyl(fever_treatment, test_malaria)
# If tested for malaria, is there a result?
fever %>% tabyl(test_malaria, result_malaria)

```

# Did those with fever seek treatment?

```{r fevtx}
# Freq table
sttx <- fever %>% tabyl(fever_treatment) %>%
  mutate(percent = percent*100)

# Plot
ggplot(sttx, aes(x = fever_treatment, y = percent, fill = fever_treatment)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Seek advice or treatment for fever",
       x = NULL,
       fill = NULL) +
  theme_minimal()

```

# If sought treatment, where did they seek treatment? 

```{r seektx}
# Where did you seek treatment responses
whtx <- fever %>% filter(fever_treatment == 1) %>% tabyl(treatment_place) %>%
  mutate(percent = percent*100)

ggplot(whtx, aes(x = treatment_place, y = percent, fill = treatment_place)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Where was advice or treatment for fever sought?",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 

```

# If "other" for where they sought treatment, where did they go?

```{r seekoth}
# List other responses for where they sought treatment
seekoth <- fever %>% tabyl(treatment_place_other) %>%
  na.omit() %>%
  select(treatment_place_other, n) %>%
  rename(`Outro local` = treatment_place_other)

flextable(seekoth) %>%
  set_caption(caption = "Onde você procurou tratamento, especifique outros")

```

# If they didn't seek treatment, why not?

```{r notx}
why_notx <- fever %>% filter(fever_treatment == 0) %>% tabyl(no_treatment_reason) %>%
  mutate(percent = percent*100)

ggplot(why_notx, aes(x = no_treatment_reason, y = percent, fill = no_treatment_reason)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Why did you not seek treatment?",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
# Reorder xaxis so other is at the end

```

# If other reason for not seeking treatment, what was it? 

```{r notxoth}
# List other responses for why didn't seek treatment
notxoth <- fever %>% tabyl(no_treat_reason_other) %>%
  na.omit() %>%
  select(no_treat_reason_other, n) %>%
  rename(Razão = no_treat_reason_other)

flextable(notx) %>%
  set_caption(caption = "Porque não procurou conselho ou tratamento?")

```

# How many reported being tested for malaria?

```{r maltest}
# Where did you seek treatment responses
tested <- fever %>% tabyl(test_malaria) %>%
  mutate(percent = percent*100)

ggplot(tested, aes(x = test_malaria, y = percent, fill = test_malaria)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Did you have a malaria test?",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
# Reorder xaxis
```

# What was the positivity rate? 

```{r postest}
# Where did you seek treatment responses
postest <- fever %>% filter(test_malaria == 1) %>% tabyl(result_malaria) %>%
  mutate(percent = percent*100) 

ggplot(postest, aes(x = result_malaria, y = percent, fill = result_malaria)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Malaria test results",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
# Reorder xaxis
```

# What medication did people report taking? 

```{r meds}
# Select just unique id and meds result
meds <- fever %>% select(id, med_1, med_2, med_3, med_4, med_5, med_6, med_7, med_8, med_9, med_10, med_11, med_12, med_13, med_14, med_96, med_98) %>%
  pivot_longer(!id, names_to = "medication", values_to = "count") %>%
  mutate(medication = case_when(medication == "med_1" ~ "Artemisinin-based combination therapy (tca/coartem)",
                                medication == "med_2" ~ "Sp/fansidar",
                                medication == "med_3" ~ "Chloroquine",
                                medication == "med_4" ~ "Amodiaquine",
                                medication == "med_5" ~ "Quinine met",
                                medication == "med_6" ~ "Quinine injection/iv",
                                medication == "med_7" ~ "Suppository artesunate",
                                medication == "med_8" ~ "Artesunate injection/iv",
                                medication == "med_9" ~ "Another anti-malarial",
                                medication == "med_10" ~ "Antibiotics pill/syrup",
                                medication == "med_11" ~ "Injection/iv antibiotics",
                                medication == "med_12" ~ "Other Aspirin Medications",
                                medication == "med_13" ~ "Other paracetemol medicines",
                                medication == "med_14" ~ "Other ibuprofen medications",
                                medication == "med_96" ~ "Other",
                                medication == "med_98" ~ "Do not know"))


## Trying to get percentages for numbers
meds <- meds %>% group_by(medication) %>%
  summarize(Mean = mean(count, na.rm=TRUE))

```


# Women's questionnaire

```{r wovars}
#women <- read.csv(here("raw/women.csv"))
# Join with hh deets
women <- left_join(women, tb, by = "submissions_id")



```


# Biomarkers

# Range of reported hemoglobin

# Nets

```{r netcheck}
# Check net brands for missing
nets %>% tabyl(brand_g_net_brand)

# Check % of nets observed 
nets %>% tabyl(statecolorshape_g_net_state)

# Check % of nets used last night
nets %>% tabyl(sleep_net)

# Check why not net used
nets %>% tabyl(no_sleep_net)

# Check if interviewer put in 1234 for net users:
nets_check <- nets %>% 
  mutate(netusers1234=case_when(net_users_g_user1_nb==1 & net_users_g_user2_nb==2 & net_users_g_user3_nb==3 & net_users_g_user4_nb==4 ~ "wrong",
         TRUE ~ "right"))
nets_check %>% tabyl(netusers1234)

# Check total # of nets in hh
nets %>% 
  group_by(submissions_id) %>% 
  summarize(count=max(nets_pos)) %>% 
  tabyl(count)

```



