---
title: "MIS data checks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}

#---- Load libraries (each time R restarts)
library(tidyverse)
library(janitor)
library(readxl)
library(sf)
library(openxlsx)
library(ggrepel)
library(here)
library(lubridate)
library(flextable)
library(officer)
library(labelled)
library(haven)
library(purrr)
library(haven)
library(readr)

#---- Knitr options
knitr::opts_chunk$set(echo = TRUE)


```

```{r getdata}
#--- Read in the raw data dumped into the "raw" folder by the script that pulls from the ODK server
# It is set up this way to avoid having to pull from the server every time we knit

hh <- read.csv(here("raw/hh.csv"))
hhm <- read.csv(here("raw/hhm.csv"))
women <- read.csv(here("raw/women.csv"))
births <- read.csv(here("raw/births.csv"))
#birthcheck <- read.csv(here("pratica/raw/birthcheck.csv"))
fever <- read.csv(here("raw/fever.csv"))
biomarkers <- read.csv(here("raw/biomarkers.csv"))
nets <- read.csv(here("raw/nets.csv"))

amostras<- read.csv(here("raw/amostras_malaria.csv"))



```



# Extra analisys reharding relation hh and chaldren

```{r hhcheck}


#unir base do HH e da e HHM 
hh_hhm <- left_join(hh, hhm, by = c("id" = "submissions_id"))


# filtrar onde o relation =1
hh_hhm_1 <- hh_hhm %>% 
  filter(relation == 1)

hh_hhm_2 <- hh_hhm_1 %>% 
  select(id, relation, sex, sleep, age,live, age_m, hhh, hh_nb, hh_id_field)

# unir a base hh_hhm com a base hh_null_sex_idade

base_final <- right_join(hh_hhm_2, hh_null_sex_idade, by = c("id" = "submissions_id"))


base_final_1 <- right_join(hh_hhm_2, base_rachis, by = c("id" = "submissions_id"))

write_dta(base_final_1, here("raw/base_criancas_e_hh.dta"))





```





```{r netcheck}

#-------------------------------------------------------------------------------
#CRIANCAS COM MALARIA POSITIVO
hh_hhm<- left_join(hh, hhm, by = c("id" = "submissions_id"))
hhm_biomarker<- inner_join(hhm, biomarkers, by = c("submissions_id" = "submissions_id"))
hhm_woman<- inner_join(hhm, women, by = c("submissions_id" = "submissions_id"))
woman_fever<- inner_join(women, fever, by = c("submissions_id" = "submissions_id"))


dfs <- list(hh_hhm = hh_hhm, hhm_biomarker = hhm_biomarker, hhm_woman = hhm_woman, woman_fever = woman_fever)
dfs <- list(hh = hh, hhm = hhm, nets = nets, women = women, births = births, fever = fever, biomarkers = biomarkers)
# Make all of them dataframes instead of tibbles:
dataframe_list <- lapply(dfs, as.data.frame)

# Export csv copies of the raw data
walk2(dataframe_list, paste0("raw/", names(dataframe_list), ".csv"), write_csv)

Malaria_p<- Malaria_teste %>% 
  filter(end_survey > "2023-11-01",
         start_survey > "2023-11-01")



Malaria_p_gaza<- Malaria_p %>% 
  filter(malaria_result == 1)

#remover Duplicado baseandose na variavel name_child_biom
Malaria_p_gaza<-Malaria_p_gaza %>% distinct(name_child_biom, .keep_all = TRUE)


View(Malaria_p_gaza)

malar_pos_gaza_last <- Malaria_p_gaza %>% 
  filter(end_survey > "2024-01-01",
         start_survey > "2024-01-01")
dim(malar_pos_gaza_last)
view(malar_pos_gaza_last)

view(Malaria_p_gaza %>% select(name_child_biom, tdr_malaria))
write.csv(malar_pos_gaza_last, here("raw/Malaria_pos_gaza_last.csv"))

#selecionar provincia 9
Malaria_p_gaza<- Malaria_p_gaza %>% 
  filter(province == 9)
view(Malaria_p_gaza)
dim(Malaria_p_gaza)




Malaria_maputo<- Malaria_p %>% 
  filter(province == 10)
Malaria_maputo<- Malaria_maputo %>% 
  filter(tdr_malaria == 1)

Malaria_mcidade<- Malaria_p %>% 
  filter(province == 11)

Malaria_mcidade<- Malaria_mcidade %>% 
  filter(tdr_malaria == 1)

dim(Malaria_p_gaza)
dim(Malaria_maputo)
dim(Malaria_mcidade)
dim(fever)

view(Malaria_p_gaza %>% select(name_child_biom, tdr_malaria))

#exportar base de gaza positivos
write.csv(Malaria_p_gaza, here("raw/Malaria_posit_Gaza.csv"))

# get surveyor start date
hh_join_check <- hh_join_check %>% 
  filter(end_survey > "2023-11-01",
         start_survey > "2023-11-01")

str(Malaria_p_gaza)

# Write data to csv
write.csv(hh_join_check, here("raw/hh_join_check.csv"))

#-------------------------------------------------------------------------------

dim(hh)
dim(women)

#combine hh and woman by submission id
db_hh_woman<- left_join(hh,women, by = c("id" = "submissions_id"))

dim(db_hh_woman)
view(db_hh_woman)

```

```{r setup}


# Set up small dataframe with hh details to add to other datasets
tb <- hh %>% select(id, surveyor_id, area, local, hh_nb, hh_id_field, date_today) %>%
  rename(submissions_id = id) # rename uuid to match the names in the repeat dataframes
tb$date_today <- as.Date(ymd_hms(tb$date_today))  # Fix date format

```

# Household data

```{r hhcheck}
#---- Household checks -----
hh_check <- hh %>% 
  mutate(starttime=as_datetime(start_survey),
         endtime=as_datetime(end_survey),
         startdate=date(starttime),
         enddate=date(endtime)) 

hh_check %>%  
  tabyl(startdate) 
hh_check %>% 
  tabyl(enddate)

# Check interviewer numbers
hh %>% tabyl(surveyor_id)
hh %>% tabyl(area)

# Check duplicate hhids
dupes <- hh_check %>%
  filter(startdate>"2023-10-3") %>% 
  group_by(hh_id_field) %>%
  filter(n()>1) %>%
  ungroup()

# Check head of household names in the duplicate HHIDs
dupes %>% tabyl(hhh)

# Check # of mosq nets
hh %>% tabyl(nb_mosq_nets)

hh %>% tabyl(nonet_g_no_net_reason) 

hh %>% tabyl(final_comments)

# Does surveyor ID digit line up with hh ID number - problem with tablets going backwards/forwards

```

# Household members

```{r hhmcheck}

#----- Household Member Checks ----

# Join with hh details
hhm <- left_join(hhm, tb, by = "submissions_id")

hhm %>% tabyl(sex)
hhm %>% tabyl(live)
hhm %>% tabyl(age) # maybe an age pyramid? Check for 98s
hhm %>% tabyl(fever)
hhm %>% tabyl(travel)

```

# Fever

```{r fevars}
#fever <- read.csv(here("raw/fever.csv"))
# Join with hh details
fever <- left_join(fever, tb, by = "submissions_id")
# Remove testing data
fever <- fever %>% filter(date_today > as.Date("2023-10-02"))

```

```{r fevcheck}
#--- Data quality check
# If sought treatment, location of treatment
fever %>% tabyl(fever_treatment, treatment_place)
#expss::cross_cases(fever, fever_treatment, treatment_place)
# Did they have a malaria test if they didn't seek treatment?
fever %>% tabyl(fever_treatment, test_malaria)
# If tested for malaria, is there a result?
fever %>% tabyl(test_malaria, result_malaria)

```

# Did those with fever seek treatment?

```{r fevtx}
# Freq table
sttx <- fever %>% tabyl(fever_treatment) %>%
  mutate(percent = percent*100)

# Plot
ggplot(sttx, aes(x = fever_treatment, y = percent, fill = fever_treatment)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Seek advice or treatment for fever",
       x = NULL,
       fill = NULL) +
  theme_minimal()

```

# If sought treatment, where did they seek treatment? 

```{r seektx}
# Where did you seek treatment responses
whtx <- fever %>% filter(fever_treatment == 1) %>% tabyl(treatment_place) %>%
  mutate(percent = percent*100)

ggplot(whtx, aes(x = treatment_place, y = percent, fill = treatment_place)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Where was advice or treatment for fever sought?",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 

```

# If "other" for where they sought treatment, where did they go?

```{r seekoth}
# List other responses for where they sought treatment
seekoth <- fever %>% tabyl(treatment_place_other) %>%
  na.omit() %>%
  select(treatment_place_other, n) %>%
  rename(`Outro local` = treatment_place_other)

flextable(seekoth) %>%
  set_caption(caption = "Onde você procurou tratamento, especifique outros")

```

# If they didn't seek treatment, why not?

```{r notx}
why_notx <- fever %>% filter(fever_treatment == 0) %>% tabyl(no_treatment_reason) %>%
  mutate(percent = percent*100)

ggplot(why_notx, aes(x = no_treatment_reason, y = percent, fill = no_treatment_reason)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Why did you not seek treatment?",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
# Reorder xaxis so other is at the end

```

# If other reason for not seeking treatment, what was it? 

```{r notxoth}
# List other responses for why didn't seek treatment
notxoth <- fever %>% tabyl(no_treat_reason_other) %>%
  na.omit() %>%
  select(no_treat_reason_other, n) %>%
  rename(Razão = no_treat_reason_other)

flextable(notxoth) %>%
  set_caption(caption = "Porque não procurou conselho ou tratamento?")

```

# How many reported being tested for malaria?

```{r maltest}
# Where did you seek treatment responses
tested <- fever %>% tabyl(test_malaria) %>%
  mutate(percent = percent*100)

ggplot(tested, aes(x = test_malaria, y = percent, fill = test_malaria)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Did you have a malaria test?",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
# Reorder xaxis
```

# What was the positivity rate? 

```{r postest}
# Where did you seek treatment responses
postest <- fever %>% filter(test_malaria == 1) %>% tabyl(result_malaria) %>%
  mutate(percent = percent*100) 

ggplot(postest, aes(x = result_malaria, y = percent, fill = result_malaria)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste("n =", n, sep = " "), vjust = -0.5)) +
  ylim(0, 100) +
  labs(title = "Malaria test results",
       x = NULL,
       fill = NULL) +
  theme_minimal() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
# Reorder xaxis
```

# What medication did people report taking? 

```{r meds, eval = FALSE}
## Trying to get percentages for numbers
meds <- meds %>% group_by(medication) %>%
  summarize(Mean = mean(count, na.rm=TRUE))

```

# Women's questionnaire

```{r womencheck}
#women <- read.csv(here("raw/women.csv"))
# Join with hh deets
women <- left_join(women, tb, by = "submissions_id")

# Any duplicate women's id?
dupes <- women %>%
  group_by(women_id) %>%
  filter(n()>1) %>%
  ungroup()

# Took SP/F during revent pregnancy?
women %>% tabyl(birth_recent, preg_spf)
# How many times did she report taking SP?
hist(women$preg_spf_nb)

```







# Biomarkers

# Range of reported hemoglobin

# Nets

```{r netcheck}
# Check net brands for missing
nets %>% tabyl(net_brand)

# Check % of nets observed 
nets %>% tabyl(net_state)

# Check % of nets used last night
nets %>% tabyl(sleep_net)

# Check why not net used
nets %>% tabyl(no_sleep_net)

# Check if interviewer put in 1234 for net users:
nets_check <- nets %>% 
  mutate(netusers1234=case_when(user1_nb==1 & user2_nb==2 & user3_nb==3 & user4_nb==4 ~ "wrong",
         TRUE ~ "right"))
nets_check %>% tabyl(netusers1234)

# Check total # of nets in hh
nets %>% 
  group_by(submissions_id) %>% 
  summarize(count=max(nets_pos)) %>% 
  tabyl(count)

```


```{r sampling}
# Create table of sampling by area as requested by Anisio
# Area ID, Number of AF listed, Number of AF visited, Number of kids tested, Number of women

# NB: Listed file will have all households even if they fall outside of the enumeration area as those are dropped later in the listing process
listed <- read.csv(here("raw/listed.csv"))
# Number of households listed by area (cluster)
listed <- listed %>% tabyl(area) %>%
  rename(Listed_AF = n) %>%
  select(area, Listed_AF)

# Number of households sampled by area
sampled <- hh %>% tabyl(area) %>%
  rename(Sampled_AF = n) %>%
  select(area, Sampled_AF)

# Number of u5s
uf <- hhm %>% filter(under_5 == 1) %>%
  tabyl(area) %>%
  rename(Under5_n = n) %>%
  select(area, Under5_n)

# Number of eligible women
eligw <- hhm %>% filter(w_btw_15_49 == 1) %>%
  tabyl(area) %>%
  rename(Eligw_n = n) %>%
  select(area, Eligw_n)

# There's definitely a better way to do this but it'll do for now

# Combine listed and sampled, keep all rows even if area doesn't match up
amostra <- full_join(listed, sampled, by = "area") %>%
  full_join(uf, by = "area") %>%
  full_join(eligw, by = "area") %>%
  arrange(area)

# Write to Excel and make it pretty
# Add column headers requested by Anisio
amostra <- amostra %>% rename(`ID` = area,
                              `Número de AFs Listados` = Listed_AF,
                              `Número de AFs Visitados` = Sampled_AF,
                              `Número de Crianças 6-59 meses testadas` = Under5_n,
                              `Número de Mulheres de 15-49 anos entrevistadas` = Eligw_n)

## Create a new workbook
wb <- createWorkbook()

## Add a worksheet
addWorksheet(wb, "overview")

## set column widths
setColWidths(wb, 1, cols = 1:5, widths = c(15, 25, 25, 25, 25))

## write the data
writeData(wb, sheet = 1, x = amostra)

## Set the styles and textwrap
bodyStyle <- createStyle(fontSize=12, border="TopBottomLeftRight", borderColour = "black" , wrapText=TRUE)
headerStyle <- createStyle(fontSize=14, border="TopBottomLeftRight", borderColour = "black", wrapText=TRUE, textDecoration="bold", fgFill="darkgray")

addStyle(wb, sheet = 1, bodyStyle, rows = 1:nrow(amostra)+1, cols = 1:5, gridExpand = TRUE)
addStyle(wb, sheet = 1, headerStyle, rows = 1, cols = 1:5, gridExpand = TRUE)

## Save workbook in the "Selected" folder
saveWorkbook(wb, "Sampling summary.xlsx", overwrite = TRUE) 




testes_malaria<-c()

```




